Information is Not Communicated Uniformly: Evidence from Spoken and Written Corpora

### 2019-01-25 cogsci/position-info.Rmd
working on Cogsci submission: bibtex drafted, clustering table here

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(xtable)
```

@@

When people communicate in speaking or writing, they can have a variety of different goals. Perhaps the most important of these goals is to communicate information. If we take this as the primary goal of communication, then how information is transmitted should have regular properties. From Shannon (1948), we know that when information is being communicated, the rate of information transmission should be constant and as close as possible to the capacity of the communication channel to optimally transmit the information. Levy & Jaeger (2007) introduce the *uniform information density* (UID) hypothesis, arguing that speakers structure utterances so as to optimize information density. Viewing human communication as a noisy channel, the authors argue that speakers and writers should attempt to communicate information as evenly as possible and as close to the channel capacity as possible. Their evidence concerns the use or lack of use of “that”-complementizers in introducing English relative clauses. When the word preceding the relative clause or the initial word of the relative clause has high information content, then the authors argue that speakers are more likely to use the complementizer. The authors use adult-adult conversations from the Penn Treebank corpus.

UID has been applied broadly over the past decade, to determining whether linguistic alignment takes place (Jaeger & Snider, 2013), Zipfian word length distributions (Piantadosi et al., 2011), communication efficiency (Mahowald et al., 2013), dialogue and turn-taking (Xu & Reitter, 2018) and the significance of ambiguity in language (Piantadosi et al., 2012), among other research.

However, some recent work has contradicted the UID hypothesis. Zhan and Levy (2018) study Mandarin Chinese classifier use for specific and general Mandarin classifiers. Specific classifiers are specific to certain nouns, and UID would predict that specific classifiers would appear when the production of the corresponding noun is easier, to spread the information contained by the classifier and noun less densely over time. General classifiers can be applied to any noun and contain no special information content. Zhan and Levy find that speakers use specific classifiers  more often in cases where the production of the corresponding noun is more difficult than when the production is easier; speakers do not avoid unexpected peaks in information content for their listeners, but instead maximize their ease of production.

What Zhan and Levy (2018) and most work in favor of UID have in common is they focus on information distribution at particular points in a sentence. By contrast, Jain et al. (2018) examines word order across sentences in Hindi, a freer word order language than English, and find that information density has no significant effect on word order. For this paper, we focus on the sentence level instead of specific points, following a method described in Yu et al. (2016).

Yu et al. (2016) challenges the UID hypothesis through examining the distribution of uncertainty across sentence positions within the text portion of the English-language British National Corpus (BNC). They partition the corpus by sentence length in number of words, and proceed for each sentence length $k$ within the corpus. for each word position $X$ of sentences of length $X$, let each word $w$ be a unique word occurring in position $X$ and $p(w)$ is the number of times word $w$ occurs in position $X$ divided by the number of total words that occur in position $X$ i.e. the number of sentences of length $k$. Then $p(w)$ is the probability of randomly obtaining word $w$ by choosing a word in position $X$ in sentences of length $k$.

@@

The UID hypothesis predicts that information transmission rate will tend towards uniformity in both speech and text. We begin by examining speech to determine if we obtain the entropy curve shape we expect for spoken communication. We begin with the same source as Levy & Jaeger (2007) and Jaeger (2010), the Switchboard corpus of adult telephone conversations [CITATION]. We also examine child-adult conversations in the CHILDES TalkBank (Brown 1973; MacWhinney 2000) corpora database of spoken adult-child conversations in multiple languages. Children are not fully developed speakers, so we want to compare the entropy curve we obtain by computing over the utterances in the CHILDES corpora to the utterances in the adult-adult Switchboard corpus.

@@

Switchboard

We first used the Brown and Providence English corpora from CHILDES. The Brown corpus contains individual recordings of conversations between three children between 1.5 and 6-years-old and their families in their homes. The Providence corpus recorded interactions between children between 1 and 3 years old and their parents in the home. We divided each corpus by speaker into child and non-child categories. We further divided the corpora by utterance length, so that all sentences of length $k$ (e.g. $6$) were grouped together. Finally, within each utterance length, we computed the unigram entropy measure for each position.

In the English CHILDES corpora. The entropy curves capture individual variation across positions in utterances of the same length. This allows us to directly observe and judge the amount of variation in words that appear in an individual position of a sentence. For speech data, which for the corpora in the CHILDES database consists of short and often disconnected utterances across hours of recordings, the unigram entropy measure is unaffected by context or lack thereof in utterances by the adults and children in the corpora. We can directly compare any two positions within utterances to determine the amount of uncertainty, and therefore information, on average contained by words within that position of utterances. We are applying the same approach as in Genzel and Charniak (2003), but within sentences instead of across sentences.

@@

RESULTS OF GLM BELOW.

@@

```{r}
# References will be generated automatically by Pandoc and included here.
# The following code is some latex to format the bibliography. Do not remove it.
```

>>>>

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(xtable)
library(knitr)
```

@@

Perhaps the most important reason people talk and write to one another is to give information. From Shannon (1948), we know that when information is being communicated, the rate of information transmission should be constant and as close as possible to the capacity of the communication channel to optimally transmit the information. Levy & Jaeger (2007) introduce the *uniform information density* (UID) hypothesis, arguing that people unconsciously structure their speech and writing to communicate information at a constant, optimal rate. Levy & Jaeger (2007) argue that speakers and writers should attempt to communicate information as evenly as possible and as close to the channel capacity as possible. Their evidence concerns the use or lack of use of “that”-complementizers in introducing English relative clauses. When the word preceding the relative clause or the initial word of the relative clause has high information content, then the authors argue that speakers are more likely to use the complementizer. The authors use adult-adult conversations from the Penn Treebank corpus.

UID has been applied broadly over the past decade, to determining whether linguistic alignment takes place (Jaeger & Snider, 2013), Zipfian word length distributions (Piantadosi et al., 2011), communication efficiency (Mahowald et al., 2013), dialogue and turn-taking (Xu & Reitter, 2018) and the significance of ambiguity in language (Piantadosi et al., 2012), among other research. However, other recent work has contradicted the UID hypothesis. Zhan and Levy (2018) study Mandarin Chinese classifier use for specific and general Mandarin classifiers. Specific classifiers are specific to certain nouns, and UID would predict that specific classifiers would appear when the production of the corresponding noun is easier, to spread the information contained by the classifier and noun less densely over time. General classifiers can be applied to any noun and contain no special information content. Zhan and Levy find that speakers use specific classifiers more often in cases where the production of the corresponding noun is more difficult than when the production is easier; speakers do not avoid unexpected peaks in information content for their listeners, but instead maximize their ease of production.

Similar to the original Levy & Jaeger (2007), Zhan and Levy (2018) focuses on information distribution at particular points in a sentence. By contrast, Jain et al. (2018) examine word order across spoken sentences in Hindi, a freer word order language than English, and find that information density has no significant effect on word order. For this paper, we focus on the sentence level instead of specific points, following a method described in Yu et al. (2016).

Yu et al. (2016) challenges the UID hypothesis through examining an entropy measure across sentence positions within the text portion of the English-language British National Corpus (BNC). They partition the corpus by sentence length in number of words. For each word position $X$ of sentences of length $k$, they define $w$ as a unique word occurring in position $X$. They define $p(w)$ as the number of times word $w$ occurs in position $X$ divided by the number of total words that occur in position $X$ i.e. the number of sentences of length $k$. Then $p(w)$ is the probability of obtaining word $w$ by choosing a word at random in position $X$ in sentences of length $k$.

@@

The UID hypothesis predicts that information transmission rate will tend towards uniformity in both speech and text. We begin by examining speech to determine if we obtain the entropy curve shape we expect for spoken communication. We begin with the same source as Levy & Jaeger (2007) and Jaeger (2010), the Switchboard corpus of adult telephone conversations [CITATION]. We also examine child-adult conversations in the CHILDES TalkBank (Brown 1973; MacWhinney 2014) corpora database of spoken adult-child conversations in multiple languages. Children are not fully developed speakers, so we want to compare the entropy curve we obtain by computing over the utterances in the CHILDES corpora to the utterances in the adult-adult Switchboard corpus.

@@

Switchboard [To be put in]

We used the Brown and Providence English corpora from CHILDES. The Brown corpus contains individual recordings of conversations between three children between 1.5 and 6-years-old and their families in their homes. The Providence corpus recorded interactions between children between 1 and 3 years old and their parents in the home. We divided each corpus by speaker into child and non-child categories. We further divided the corpora by utterance length, so that all sentences of length $k$ (e.g. $6$) were grouped together. Finally, within each utterance length, we computed the unigram entropy measure for each position.

In the English CHILDES corpora. The entropy curves capture individual variation across positions in utterances of the same length. This allows us to directly observe and judge the amount of variation in words that appear in an individual position of a sentence. For speech data, which for the corpora in the CHILDES database consists of short and often disconnected utterances across hours of recordings, the unigram entropy measure is unaffected by context or lack thereof in utterances by the adults and children in the corpora. We can directly compare any two positions within utterances to determine the amount of uncertainty, and therefore information, on average contained by words within that position of utterances. We are applying the same approach as in Genzel and Charniak (2002), but within sentences instead of across sentences.

@@

```{r tables}
glm_model <- read.csv("glm.csv")
knitr::kable(glm_model)
```

@@

```{r}
# References will be generated automatically by Pandoc and included here.
# The following code is some latex to format the bibliography. Do not remove it.

```

### 2019-01-25 cogsci/position-info.tex
working on Cogsci submission: bibtex drafted, clustering table here

\title{A Language's Unigram Entropy Distribution Predicts Self-Paced Reading
Times}

@@

\begin{abstract}
A major line of research in the cognitive sciences has asked how
speakers and writers distribute information in the linguistic material
they produce. We provide evidence against the Uniform Information
Density hypothesis (Jaeger, 2010) which proposes that information is
transmitted at a constant rate close to channel capacity in human
communication. We instead argue that the information structure and
transmission rate in human communication varies predictably from
language to language based on phonological and syntactic features. We
draw evidence from written and spoken corpora, including corpora of
parent and child communication at various ages and large-scale online
corpora from Wikipedia in a typologically diverse collection of
languages.

@@

How do people convey information in speech and text? Is there a regular
distribution to how information is conveyed across speech and text? Does
speech, with its phonological properties, different from writing, with
its semiotic properties, in how information is conveyed?

A major line of research in the current century has asked how speakers
and writers distribute information in the linguistic material they
produce. This begins with Claude Shannon in the years after World War
II. Shannon (1948) defined ``information'' as a ``reduction in
uncertainty''. Shannon followed by quantifying uncertainty in his
measure of \emph{entropy}: the amount of uncertainty on the outcome of a
random variable. Shannon proposed that the most efficient method of
sending information through a noisy channel is at a constant rate.
Genzel \& Charniak (2002) apply this principle to human communication:
if people communicate information through speech and text optimally,
then we should transmit information to one another at a constant rate.
Genzel \& Charniak created a distribution of estimates for
sentence-level entropy, each sentence taken without context, for
newspaper articles from the Penn Treebank corpus. Obtaining a roughly
monotonically increasing linear distribution, Genzel \& Charniak
proposed the \emph{Constant Entropy Rate} (CER) principle: the entropy
rate in speech and text with context should be constant as sentence
number increases. Aylett \& Turk (2004) proposed a similar principle for
the phonological level.

Jaeger (2010) extends the CER principle to all levels of human
communication: the \emph{Uniform Information Density} (UID) hypothesis.
Jaeger argues that speakers will try to distribute information more
evenly over the course of an utterance, to be as close to channel
capacity (in a Shannon sense) as possible. In particular, Jaeger singles
out the production of ``that'' at the beginning of relative clauses in
English and the use of contractions such as ``he's'' and ``you're''
versus ``he is'' and ``you are'' as instances where higher information
density in the clause elicits the production of more material by
speakers.

More recent work has stood out in contrast to the traditional UID
perspective. Zhan and Levy (2018) study Mandarin Chinese classifier use,
and find that the use of specific classifiers, versus general
classifiers, appears more often in cases where the production of the
corresponding noun is more difficult than when the production is easier,
as would be predicted by UID. The UID perspective is challenged in Yu et
al. (2016), by performing an analysis of entropy by position within
sentence in the text portion of the British National Corpus. This work
serves as the basis for ours.

\section{Methods}\label{methods}

To explore information transmission rate in speech, we used the CHILDES
TalkBank (Brown 1973; MacWhinney 2000) corpora database of spoken
adult-child conversations. We first used the Brown and Providence
English corpora from CHILDES. The Brown corpus contains individual
recordings of conversations between three children between 1.5 and
6-years-old and their families in their homes. The Providence corpus
recorded interactions between children between 1 and 3 years old and
their parents in the home. We divided each corpus by speaker into child
and non-child categories. We further divided the corpora by utterance
length, so that all sentences of length \(k\) (e.g. \(6\)) were grouped
together. Finally, within each utterance length, we computed the unigram
entropy measure for each position. We follow Yu et al. (2016) in using
the following formula for each word position X of sentences of fixed
length k from the corpus, where each \(w\) is a word occurring in
position \(X\) and \(p(w)\) is the number of times word \(w\) occurs in
position X divided by the number of total words that occur in position
\(X\) i.e.~the number of sentences of length \(k\).

\[H(X) = \sum\limits_w p(w)\log\big(p(w)\big)\]

The result of this method can be plotted for each utterance length as an
\emph{entropy curve}, which can be visually compared across utterance
length to observe the how the unigram entropy changes across absolute
positions in each of the utterances in the English CHILDES corpora. The
entropy curves capture individual variation across positions in
utterances of the same length. This allows us to directly observe and
judge the amount of variation in words that appear in an individual
position of a sentence. For speech data, which for the corpora in the
CHILDES database consists of short and often disconnected utterances
across hours of recordings, the unigram entropy measure is unaffected by
context or lack thereof in utterances by the adults and children in the
corpora. We can directly compare any two positions within utterances to
determine the amount of uncertainty, and therefore information, on
average contained by words within that position of utterances. We are
applying the same approach as in Genzel and Charniak (2003), but within
sentences instead of across sentences.

@@

We also ran this analysis on Spanish, German, Mandarin and Japanese
corpora from CHILDES. We used the Shiro corpus for Spanish (Shiro,
2000), which contains prompted narratives individually collected from
over a hundred Venezualan schoolchildren, half from high SES backgrounds
and half from low SES backgrounds. The German corpus we used was the
Wagner corpus of spontaneous parent-child speech in the home, collected
in single sessions for children between 1 and 14 years of age (Wagner,
1985). We used the Zhou dinner corpus for Mandarin Chinese (Li \& Zhou,
2015), which contains dinner conversations between 5 to 6-year-old
children and their parents collected in Shanghai. We used the Okayama
corpus for Japanese (Okayama, 1973), which consists of conversations
between 2 to 4-year-old children and their mothers in single sessions.

For each corpus, we accessed transcripts of the corpus provided through
the TalkBank system and computed over Roman alphabet transcriptions or
transliterations of the original transcriptions. For Mandarin, we used
pinyin transliterations of the utterances in the corpus with demarcated
word boundaries, and for Japanese we used romanji (Roman alphabet)
transliterations of words in the corpus. Japanese Hiragana, Katakana and
Kanji writing systems, and the Chinese characters used for writing
Mandarin do not normally demarcate word boundaries by spacing words
apart, and for normal Japanese and Chinese writing including spaces
between word boundaries can have a negative effect on reading times
(Sainio et al, 2007; Bai et al, 2008).

@@

{\centering \includegraphics{figs/wagner_PE-1}

\caption[Wagner corpus unigram entropy]{Wagner corpus unigram entropy}\label{fig:wagner_PE}
\end{figure*}
\end{CodeChunk}

@@

{\centering \includegraphics{figs/okayama_PE-1}

\caption[Okayama corpus unigram entropy]{Okayama corpus unigram entropy}\label{fig:okayama_PE}
\end{figure*}
\end{CodeChunk}

\section{Results \& Analysis}\label{results-analysis}

The Unigram Information Density account would predict that children have
a lower channel capacity for communication and would instead communicate
with a less unigram entropy curve. The adult and child entropy curves
track one another almost identically. This not only indicates a
robustness in the unigram entropy curve across speakers, but also across
ages and addressees. We also observed a robustness across corpora for
the same languages, and a robustness across utterance lengths within the
same corpus's entropy curve. This shows that the concept of an ``entropy
curve'' for a specific language is well-founded when considering speech
data.

We found a distinct three-step distribution for English, Spanish and
German CHILDES corpora, with a slight dip in the penultimate position of
each sentence. We attribute the penultimate dip in these unigram entropy
curves to the fact that most of the utterances in the CHILDES English,
Spanish and German corpora we examined had a determiner such as ``the''
or ``a'' in the second-to-last position of utterances. The beginnings of
utterances in the English, German and Spanish CHILDES data were usually
pronouns or grammatical subjects, while the final words were grammatical
objects and had a great deal of variation in the exact word that
appeared in the utterance-final position. The final position of
utterances in child-directed speech is known to be important, dating
back to Aslin (1993). The Mandarin and Japanese data, by comparison,
have noticeably lower positional entropy values in utterance-final
positions than in utterance-penultimate positions. The Japanese entropy
curve begins high and then drops, unlike all of the other entropy
curves.

{\centering \includegraphics{figs/MI_wagner-1}

\caption[Mutual Information measures on utterances of length 6 in the Wagner corpus]{Mutual Information measures on utterances of length 6 in the Wagner corpus}\label{fig:MI_wagner}
\end{figure*}
\end{CodeChunk}

{\centering \includegraphics{figs/MI_okayama-1}

\caption[Mutual Information measures on utterances of length 6 in the Okayama corpus]{Mutual Information measures on utterances of length 6 in the Okayama corpus}\label{fig:MI_okayama}
\end{figure*}
\end{CodeChunk}

The mutual information statistic is a symmetric measure of the
information gained about one random variable by learning about another,
a bigram measure and indicator of the effect than the context of a word
can have on its unigram entropy value. As seen in the images below, the
final word in utterances of length \(6\) in German has a significant
mutual information value with all other words in the utterance on
average. This means that the words appearing in positions \(1\) through
\(5\) all play a role in determining the word that appears in position
\(6\) and vice versa. By contrast, the words that appear in positions
\(1\) through \(4\) have little influence in determining the word that
appears in position \(5\), the penultimate word that is often a
determiner or function word, and instead the final word has the greatest
influence in determining the penultimate word. For Japanese, the final
word in an utterance has little to no influence on determining the rest
of the words and vice versa, whereas the other words all play in role in
determining what will go in each other's positions.

\section{Large-scale text data}\label{large-scale-text-data}

We also wanted to apply this analysis to large-scale text data, to
compare with the parent-child speech data results from using CHILDES.
Using Giuseppe Attardi's Wikiextractor tool
\footnote{https://github.com/attardi/wikiextractor}, we extracted the
text corpora for \(165\) languages from Wikipedia by downloading a
stored collection of Wikipedia entries in each langauge and randomly
selecting several thousand articles from each Wikipedia language. Each
language corpus was cleaned and limited to sentences between \(6\) and
\(50\) words. Similar to the data from CHILDES, we divided each corpus
by sentence length, and then computed the unigram entropy measure on
each word position within each sentence length.

@@

\subsection{Clustering}\label{clustering}

@@

{\centering \includegraphics{figs/absolute_clusters-1}

\caption[Absolute clustering of Wikipedia corpora]{Absolute clustering of Wikipedia corpora}\label{fig:absolute_clusters}
\end{figure*}
\end{CodeChunk}

\subsection{Language Features}\label{language-features}

To determine which phonological, morphological and syntactic features
affected the embedding of a language in the Wikipedia dataset, we looked
at the list of \(144\) linguistic features in World Atlas of Language
Structures (Dryer \& Haspelmath, 2013). We limited the languages in the
WALS database to only those in our Wikipedia dataset and performed
missing-value imputation to obtain the features not coded in WALS for
the languages from Wikipedia. We then performed k-modes clustering and
compared the results with the hierarchical clustering from Wikipedia.
{[}Still working on this{]}

We also checked the effects of individual features on the embeddings of
languages in the different treatments. {[}Still working on this{]}

>>>>

\title{Information is Not Communicated Uniformly: Evidence from Spoken and
Written Corpora}

@@

\begin{abstract}
We provide evidence against the popular Uniform Information Density
hypothesis (Levy \& Jaeger, 2007) which proposes that information is
transmitted at a constant rate close to channel capacity in human
communication. Using a method based on the original Genzel \& Charniak
(2002) entropy measure, we construct a word-level model for entropy
applicable to both spoken and written corpora. We apply this model to
corpora from Wikipedia in well over a hundred languages. We find that
not only is the Uniform Information Density hypothesis prediction wrong,
but also that the by-word entropy distribution of a language is related
to the typological features of the language. We use this evidence to
suggest that people do not communicate information at a uniform rate,
but that information distribution varies from language to language based
on phonogical, morphological and syntactic features.

@@

Perhaps the most important reason people talk and write to one another
is to give information. From Shannon (1948), we know that when
information is being communicated, the rate of information transmission
should be constant and as close as possible to the capacity of the
communication channel to optimally transmit the information. Levy \&
Jaeger (2007) introduce the \emph{uniform information density} (UID)
hypothesis, arguing that people unconsciously structure their speech and
writing to communicate information at a constant, optimal rate. Levy \&
Jaeger (2007) argue that speakers and writers should attempt to
communicate information as evenly as possible and as close to the
channel capacity as possible. Their evidence concerns the use or lack of
use of ``that''-complementizers in introducing English relative clauses.
When the word preceding the relative clause or the initial word of the
relative clause has high information content, then the authors argue
that speakers are more likely to use the complementizer. The authors use
adult-adult conversations from the Penn Treebank corpus.

UID has been applied broadly over the past decade, to determining
whether linguistic alignment takes place (Jaeger \& Snider, 2013),
Zipfian word length distributions (Piantadosi et al., 2011),
communication efficiency (Mahowald et al., 2013), dialogue and
turn-taking (Xu \& Reitter, 2018) and the significance of ambiguity in
language (Piantadosi et al., 2012), among other research. However, other
recent work has contradicted the UID hypothesis. Zhan and Levy (2018)
study Mandarin Chinese classifier use for specific and general Mandarin
classifiers. Specific classifiers are specific to certain nouns, and UID
would predict that specific classifiers would appear when the production
of the corresponding noun is easier, to spread the information contained
by the classifier and noun less densely over time. General classifiers
can be applied to any noun and contain no special information content.
Zhan and Levy find that speakers use specific classifiers more often in
cases where the production of the corresponding noun is more difficult
than when the production is easier; speakers do not avoid unexpected
peaks in information content for their listeners, but instead maximize
their ease of production.

Similar to the original Levy \& Jaeger (2007), Zhan and Levy (2018)
focuses on information distribution at particular points in a sentence.
By contrast, Jain et al. (2018) examine word order across spoken
sentences in Hindi, a freer word order language than English, and find
that information density has no significant effect on word order. For
this paper, we focus on the sentence level instead of specific points,
following a method described in Yu et al. (2016).

Yu et al. (2016) challenges the UID hypothesis through examining an
entropy measure across sentence positions within the text portion of the
English-language British National Corpus (BNC). They partition the
corpus by sentence length in number of words. For each word position
\(X\) of sentences of length \(k\), they define \(w\) as a unique word
occurring in position \(X\). They define \(p(w)\) as the number of times
word \(w\) occurs in position \(X\) divided by the number of total words
that occur in position \(X\) i.e.~the number of sentences of length
\(k\). Then \(p(w)\) is the probability of obtaining word \(w\) by
choosing a word at random in position \(X\) in sentences of length
\(k\).

\[H(X) = \sum\limits_w p(w)\log\big(p(w)\big)\] With this measure, Yu et
al. compute the unigram entropy at each position of sentences of each
length within the corpus. The result of this method can be plotted for
each utterance length as an \emph{entropy curve}, which can be visually
compared across utterance length to observe the how the unigram entropy
changes across absolute positions in each of the utterances. Genzel \&
Charniak (2002) similarly examine a unigram entropy measure on
sentences, and found that entropy at the sentence level increases
linearly with sentence index within a corpus. UID applies this
uniformity of entropy rate in sentences to all levels of speech, and so
the Yu et al. method, which examines text at the word level, should find
an affine function at the word level.

Let us assume that the UID perspective is correct. Then we expect that
the entropy curve for every language should be close to an affine,
linear function with some noise. Entropy should monotonically and
uniformly increase at all word positions across utterances on average.
We will find a contradiction with this claim through examining the
average entropy at each position of a sentence for both speech and text
data.

\section{Spoken data}\label{spoken-data}

The UID hypothesis predicts that information transmission rate will tend
towards uniformity in both speech and text. We begin by examining speech
to determine if we obtain the entropy curve shape we expect for spoken
communication. We begin with the same source as Levy \& Jaeger (2007)
and Jaeger (2010), the Switchboard corpus of adult telephone
conversations {[}CITATION{]}. We also examine child-adult conversations
in the CHILDES TalkBank (Brown 1973; MacWhinney 2014) corpora database
of spoken adult-child conversations in multiple languages. Children are
not fully developed speakers, so we want to compare the entropy curve we
obtain by computing over the utterances in the CHILDES corpora to the
utterances in the adult-adult Switchboard corpus.

\subsection{Methods}\label{methods}

Switchboard {[}To be put in{]}

We used the Brown and Providence English corpora from CHILDES. The Brown
corpus contains individual recordings of conversations between three
children between 1.5 and 6-years-old and their families in their homes.
The Providence corpus recorded interactions between children between 1
and 3 years old and their parents in the home. We divided each corpus by
speaker into child and non-child categories. We further divided the
corpora by utterance length, so that all sentences of length \(k\) (e.g.
\(6\)) were grouped together. Finally, within each utterance length, we
computed the unigram entropy measure for each position.

In the English CHILDES corpora. The entropy curves capture individual
variation across positions in utterances of the same length. This allows
us to directly observe and judge the amount of variation in words that
appear in an individual position of a sentence. For speech data, which
for the corpora in the CHILDES database consists of short and often
disconnected utterances across hours of recordings, the unigram entropy
measure is unaffected by context or lack thereof in utterances by the
adults and children in the corpora. We can directly compare any two
positions within utterances to determine the amount of uncertainty, and
therefore information, on average contained by words within that
position of utterances. We are applying the same approach as in Genzel
and Charniak (2002), but within sentences instead of across sentences.

@@

We also ran this analysis on Spanish and Mandarin corpora from CHILDES.
We used the Shiro corpus for Spanish (Shiro, 2000), which contains
prompted narratives individually collected from over a hundred
Venezualan schoolchildren, half from high SES backgrounds and half from
low SES backgrounds. We used the Zhou dinner corpus for Mandarin Chinese
(Li \& Zhou, 2015), which contains dinner conversations between 5 to
6-year-old children and their parents collected in Shanghai.

For each corpus, we accessed transcripts of the corpus provided through
the TalkBank system and computed over Roman alphabet transcriptions or
transliterations of the original transcriptions. For Mandarin, we used
pinyin transliterations of the utterances in the corpus with demarcated
word boundaries, and for Japanese we used romanji (Roman alphabet)
transliterations of words in the corpus. The Chinese characters used for
writing Mandarin do not normally demarcate word boundaries by spacing
words apart, and for normal Chinese writing including spaces between
word boundaries can have a negative effect on reading times (Bai et al,
2008).

@@

@@

\subsection{Results \& Analysis}\label{results-analysis}

The adult and child entropy curves track one another almost identically.
This is surprising because UID would predict that the young children in
the corpora who are not fully developed speakers would have more noise
in their distribution of information rates. This not only indicates a
robustness in the unigram entropy curve across speakers, but also across
ages and addressees. We also observed a robustness across corpora for
the same languages, and a robustness across utterance lengths within the
same corpus's entropy curve. This shows that the concept of an ``entropy
curve'' for a specific language is well-founded when considering speech
data.

We found a distinct three-step distribution for English and Spanish
CHILDES corpora, with a slight dip in the penultimate position of each
sentence. The final position of utterances in child-directed speech is
known to be important, dating back to Aslin (1993). The Mandarin corpus
entropy curve, by comparison, has a noticeably lower positional entropy
values in utterance-final positions than in utterance-penultimate
positions.

We attribute the penultimate dip in the English and Spanish entropy
curves to the fact that most of the utterances in the CHILDES English
and Spanish corpora we examined had a determiner such as ``the'' or
``a'' in the second-to-last position of utterances. The beginnings of
utterances in the English and Spanish CHILDES data were usually pronouns
or grammatical subjects, while the final words were grammatical objects
and had a great deal of variation in the exact word that appeared in the
utterance-final position.

These entropy curves are not what would be expected from UID. The
robustness of the three-step distribution for English and its
replication in Spanish do not resemble the affine function we would
expect from UID. The Mandarin entropy curve, which does not at all
resemble either the English/Spanish distribution or the predictions of
UID, suggests that the entropy curve can vary from language to language.
UID predicts that each language should have a similar distribution.

\section{Written data}\label{written-data}

The UID hypothesis also applies to written communication: we expect
people to communicate information at a uniform rate through writing as
well. We use Wikipedia as a source for written data, which provides two
advantages. One, the quantity of data in Wikipedia is large for each
language and two, there are hundreds of languages with Wikipedias. This
allows us to perform the entropy analysis on a much greater scale and to
directly compare the results of the entropy analysis on each language to
one another, and ultimately to predict what typological features of a
language help determine its entropy curve, if any. We will describe our
method of harvesting and distilling text data from each Wikipedia as
well as how we compare the entropy curves from each language to one
another.

\subsection{Methods}\label{methods-1}

Using Giuseppe Attardi's Wikiextractor tool
\footnote{https://github.com/attardi/wikiextractor}, we extracted the
text corpora for \(165\) languages from Wikipedia by downloading a
stored collection of Wikipedia entries in each langauge and randomly
selecting several thousand articles from each Wikipedia language. Each
language corpus was cleaned and limited to sentences between \(6\) and
\(50\) words. Similar to the data from CHILDES, we divided each corpus
by sentence length, and then computed the unigram entropy measure on
each word position within each sentence length.

@@

\subsection{Results and Analysis}\label{results-and-analysis}

@@

To determine which phonological, morphological and syntactic features
affected the embedding of a language in the Wikipedia dataset, we looked
at the list of \(144\) linguistic features in World Atlas of Language
Structures (Dryer \& Haspelmath, 2013). We limited the languages in the
WALS database to only those in our Wikipedia dataset and performed
missing-value imputation to obtain the features not coded in WALS for
the languages from Wikipedia.

One approach is to cluster the languages used in the Wikipedia analysis
on the basis of WALS features and then directly compare the WALS
clustering results with the results of the hierarchical clustering on
the Wikipedia slope data for each of the different treatments using
clustering similarity evaluation methods such as the Rand index (Rand,
1971). However, the problem then arises of which combination of WALS
features and how many features to include in the clustering analysis.
This is a computationally intractable operation. Additionallly, deciding
how many clusters to use in an unsupervised clustering analysis is an
unsolved problem in machine learning.

We instead check the effects of individual features on the embeddings of
languages in the different treatments. We computed pairwise cosine
similarity between each pair of language vectors within a treatment. For
a subset of WALS features which had values entered for most of the
languages we obtained from Wikipedia, we used a generalized linear model
to see whether the cosine similarity between languages mattered in
predicting if the languages shared the same value for a WALS feature. We
found this to be true.

\begin{CodeChunk}

  X  feature   term       estimate   std.error    statistic     p.value
---  --------  -------  ----------  ----------  -----------  ----------
  1  83A       cosine    1.8386502   0.0103168   178.219026   0.0000000
  2  95A       cosine    1.8971831   0.0110958   170.981718   0.0000000
  3  81A       cosine    1.5149072   0.0098565   153.696819   0.0000000
  4  97A       cosine    1.5767216   0.0115245   136.814432   0.0000000
  5  144A      cosine    0.8782219   0.0117991    74.431427   0.0000000
  6  138A      cosine    0.3951762   0.0085684    46.120042   0.0000000
  7  87A       cosine    0.3334803   0.0083557    39.910595   0.0000000
  8  143A      cosine    0.3736337   0.0094014    39.742361   0.0000000
  9  82A       cosine    0.0298738   0.0092598     3.226171   0.0012546

\end{CodeChunk}
